### 2017-07-24 Doc/classicthesis/Chapters/Introduction.tex
tercer borrador
fix

@@

	Victor then asks to repeat the experiment. With $20$ repetitions, the chances Peggy fools Victor in all of them is only  $2^{-20}$,
	\marginpar{\includegraphics[width=1.\linewidth]{gfx/graficoJL_ZKP_3}\\The cave. Peggy returns by the requested path.}

>>>>

In traditional M2M (Machine to Machine) environments the issues about security and privacy have already been treated deeply, but in the IoT world, due to it's recent and fast growth, lacks of those tools to solve autonomously these problems.

@@

	Victor then asks to repeat the experiment. With $20$ repetitions, the chances Peggy fools Victor in all of them is only  $2^{-20}$.
	\marginpar{\includegraphics[width=1.\linewidth]{gfx/graficoJL_ZKP_3}\\The cave. Peggy returns by the requested path.}
